\chapter*{Introduction}

I expect whoever comes across this project to be, at the very least, surprised to
find out I'm keeping under the same repository a book written both in English and
in Galician; and more surprised I expect you to be when you find out hte Galician
version is, in fact, the main one.

Normally, I would just leave the question "Why in Galician?" outside of the text,
never to be adressed; but since this is going to be posted on Github, I'll try my
best to explain people who may never heard of Galician language before why I'm doing
this.

First, and more important, because it's my mother tongue. I live in a small region
in the northwest of Spain called Galicia (or Galiza, both writings are valid) and
we have a language on our own called Galician. It is a minoritary language (despite
having legal recognition) and compared to twenty or forty years ago Galician has
lost a great number of speakers; but that doesn't mean it's an extinct language.

Related to that very topic is my second reason: I find the amount of books on
numerical analysis "lacking", so to speak; as of today, the only one I know
about is Ciarlet's "Introduction to Linear Numerical Algebra and Optimisation",
which was translated from French. In order for Galician to stay alive it must
be relevant, and that implies that we continue to write science, literature,
newspapers, etc., on it. This will try to be my contribution to that goal.

Lastly, and also very related to my previous reason (it could be considered
the same, actually), English has plenty of books on numerical analysis written
by more competent mathematicians than I am. I expect you to find more helpful
or complete the books I will be referencing than my redaction of the same contents.
The only reason I keep an Egnlish translation is that maybe someone can find
an open book like this helpful, or maybe you find this project interesting
and you want to give some feedback. Whatever is your case, I thank you for
your interest.

A last word of advice: I will be focusing on the Galician version and
this is a project I will be dedicating my free time to; therefore, if
I haven't updated this project on a while, keep in mind it doesn't necessarily
mean that I have abandoned it.